%-------------------------
% Professional CV for Youssef Awad
% ATS-Optimized LaTeX Template (1 Page)
%-------------------------

\documentclass[10pt,a4paper]{article}

% Packages - minimal for ATS compatibility
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}

% ATS-friendly formatting
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% Section formatting
\titleformat{\section}{\normalsize\bfseries}{}{0em}{}[\vspace{-0.6em}\rule{\textwidth}{0.4pt}]
\titlespacing{\section}{0pt}{6pt}{3pt}

% Tight list spacing
\setlist[itemize]{leftmargin=1.2em, noitemsep, topsep=1pt, parsep=0pt}

% Hyperlink setup - no colors for ATS
\hypersetup{colorlinks=false, pdfborder={0 0 0}}

\begin{document}

%---------- HEADER ----------
\begin{center}
    {\Large \textbf{Youssef Awad}}\\[2pt]
    {\small youssef-awad@outlook.com | +971507399908 | UAE (GMT+4) | linkedin.com/in/youssef-awad | github.com/DeadPackets}
\end{center}

%---------- SUMMARY ----------
\section{Summary}
{\small Engineer who builds production systems powered by LLMs (multi-agent orchestration, RAG, evals, and autonomous agents), backed by an offensive-security foundation (OSCP). Co-founded CTFae and built the infrastructure behind the world's largest CTF: 10,000+ concurrent users, a Guinness World Record, and Best Emirati Startup at GISEC 2024. I solve real problems with code, automate the boring parts, and ship things people rely on, then threat-model them like an attacker.}

%---------- EXPERIENCE ----------
\section{Professional Experience}

{\small\textbf{Head of Engineering \& Co-Founder} | \textbf{CTFae} -- Dubai, UAE \hfill 2021 -- Present}
\begin{itemize}
    \item {\small Architected Challenge Deployment API (Python/FastAPI) for on-demand provisioning of containerized challenges to AWS ECS with auto-scaling, serving 10,000+ concurrent participants at BlackHat MEA (Guinness World Record 2024).}
    \item {\small Built CyberRanges IaC platform (Terraform, Packer, Ansible) for automated multi-VM attack-defense environments across AWS and GCP, plus CI/CD pipelines with GitHub Actions and OIDC.}
    \item {\small Developed Attack-Defense checksystem with Python/Celery, PostgreSQL (PgCat pooling), and Redis for real-time scoring of 100+ teams simultaneously.}
    \item {\small Led engineering for DEFCON 33 Bug Bounty CTF, GITEX Dubai, Bahrain National CTF, BSides Nashville, HITB, and Dubai Police CTF.}
\end{itemize}

\vspace{2pt}

{\small\textbf{Senior Cyber Security Consultant} | \textbf{Malcrove} -- Dubai, UAE \hfill 2022 -- Dec 2025}
\begin{itemize}
    \item {\small Conducted penetration testing for UAE government and critical-infrastructure clients across web/mobile applications, internal/external networks, and wireless systems.}
    \item {\small Achieved over 90\% success rate in obtaining Domain Admin privileges across 100+ Active Directory engagements.}
    \item {\small Authored CVSS-scored vulnerability reports with proof-of-concept exploits and remediation guidance; presented executive summaries to non-technical leadership.}
\end{itemize}

%---------- AI / AGENTIC PROJECTS ----------
\section{AI \& Agentic Projects}
\begin{itemize}
    \item {\small \textbf{ProjectHailMary} -- Solo-operated agentic vulnerability finder: one orchestrator drives 60+ charter-bearing subagents through a validation gauntlet (trace, PoC, CVSS, dedup) into a deterministic CLEAR/HOLD/REJECT verdict. 23 modules, 465+ tests. (Python)}
    \item {\small \textbf{LLM-AD-Defense} -- Autonomous SOC analyst on Gemini 2.5 Pro: ingests Wazuh EDR alerts and executes its own remediation, including isolating compromised Active Directory accounts. (Python/FastAPI)}
    \item {\small \textbf{LLMChessArena} (live) -- Any LLM vs any LLM over OpenRouter, with real-time WebSocket streaming, move-by-move Stockfish evaluation, and per-move token/cost tracking. (TypeScript)}
\end{itemize}

%---------- SKILLS ----------
\section{Technical Skills}
{\small
\textbf{Applied AI / LLMs:} LLM integration, multi-agent orchestration, RAG, evals \& guardrails, prompt engineering, OpenRouter, Claude, Gemini\\
\textbf{Languages:} Python, TypeScript, JavaScript, Bash, SQL\\
\textbf{Cloud/DevOps:} Docker, Terraform, Ansible, Packer, GitHub Actions, AWS (ECS, ECR, IAM), GCP\\
\textbf{Backend \& Web:} FastAPI, Hono, Flask, Express, React, Next.js, Vite, Tailwind, PostgreSQL, Redis, RabbitMQ, Celery, Pydantic, SQLAlchemy, Nginx, Linux\\
\textbf{Security:} Penetration Testing, Red Teaming, Active Directory, Vulnerability Assessment, CTF Development
}

%---------- EDUCATION ----------
\section{Education \& Certifications}
{\small
\textbf{B.Sc. Computer Engineering} (Minor: Computer Science) -- American University of Sharjah, UAE \hfill 2017 -- 2022\\
\textbf{OSCP} -- Offensive Security Certified Professional (Score: 90/100)
}

%---------- AWARDS ----------
\section{Awards}
{\small
\begin{itemize}
    \item \textbf{Guinness World Record (2024):} Largest CTF competition in the world -- BlackHat MEA
    \item \textbf{Best Community Engagement (2025):} UAE CyberSecurity Awards \quad $\bullet$ \quad \textbf{Best Emirati Startup (2024):} GISEC UAE
    \item \textbf{12+ CTF Wins:} CyberBattle of Emirates, Dubai Police CTF, CyberTalents UAE, HITB Lockdown, CyberQuest
\end{itemize}
}

\end{document}
